% Joshua McIntosh's Resume
% Based on Andrew McNabb's Resume
% Original Document Created: 7 Jan 2004
% Current Document Last Modified: Sun Sep 16 18:59:17 PDT 2012
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,oneside]{article}
\usepackage{xltxtra,fontspec,xunicode}
\usepackage{geometry}
\usepackage{hyperref}

\defaultfontfeatures{Ligatures=TeX}
\setmainfont{TeX Gyre Schola}
%\setromanfont{Tahoma}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=1in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Joshua McIntosh}
\newcommand{\addr}{Antioch, California}
\newcommand{\phone}{(925) 526 - 6308}
\newcommand{\email}{\href{http://www.linkedin.com/pub/joshua-mcintosh/57/b82/690}
{View my LinkedIn profile}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

\newfontfamily \bigtxt[]{TeX Gyre Heros}
\newfontfamily \myname[]{TeX Gyre Schola}

% This defines how the name looks
\newcommand{\bigname}[1]{
		\begin{center}\huge{\myname #1}\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\textbf{\LARGE {\bigtxt #1}}}
	\begin{itemize}
	\vspace{2pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{2.1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-2pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-4pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{0pt}
	\begin{itemize}
}{
	\end{itemize}
}



\newfontfamily \autodesk[Color=00B2EF]{TeX Gyre Bonum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

% \fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{.25pt}
\textsf{Located in \addr}\hfill \phone;\hspace{4pt}\email


\vspace{8 pt}

\begin{ressection}{Summary}
\item Linux admin and web engineer with enterprise experience; providing 
	statistics collection and automation tasks for about 1,000 servers; with
	working experince in LDAP, the LAMP stack, \texttt{yum/rpm}, facets of 
	repackaging software for \texttt{UNIX} and Linux consumption, RHEL and 
	CentOS distributions of Linux as well as Solaris 5.9 and 5.10; And 
	experience with Ruby On Rails, some PHP libraries and frameworks, as well as
	client-side and server-side javascript.
\end{ressection}
 
\begin{ressection}{Related Experience}

		\begin{ressubsec}{\href{http://usa.autodesk.com/}{\autodesk Autodesk}, Inc.}{San Rafael, CA}{December 
				2011--September 06, 2012}
				\begin{reslist}{Server Administration:}
						\resitem {assisted with day-to-day tasks such as 
						installing and maintaining software, as well as ticketed
						events, such as disk overusage or application errors}

						\resitem {Helped other engineers with projects, including 
						vulnerabilty testing, upgrading consoles, and data 
						collections.}

						\resitem {Worked on maintainence tasks across upwards of 
						1,000 servers.}

				\end{reslist}

				\begin{reslist}{Website Design and Engineering:}
						\resitem {Designed server inventory system using the
						LAMP stack and \href{http://phpsavant.com/}
						{PHP's Savant templating library}, as well as jQuery, 
						\href{http://people.iola.dk/olau/flot/examples}{Flot}, 
						and \href{http://twitter.github.com/bootstrap/index.html}
						{Twitter Bootstrap}. Site also used nagios and 
						rrdtool as a data provider.}

						\resitem {Built a proof of conecept site using 
						\href{http://angularjs.org/}{Angularjs}
						and PHP's \href{http://slimframework.com/}{Slim} 
						application, also with jQuery and Twitter 
						Bootstrap.}

						\resitem {Worked on a web interface for managing a 
						multiple-system sudoers file driven by Ruby on Rails 
						and Active Directory via ruby-ldap.}

				\end{reslist}

		\end{ressubsec}
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills/Interests}


    %%%%%%%%%%%%%%%%%%%%%%%% COMSC %%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\resitem{\textbf{Operating Systems:} Linux (Gentoo, Red Hat, and Debian), Mac OS 9 and X, UNIX (several variants), Windows 98/2000/XP}

    %%%%%%%%%%%%%%%%%%%%%%%% REG   %%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{reslist}{Computer Systems---Linux:}
		\ressubitem{Primary computing platfrom of choice is Linux, using the 
		\href{http://www.archlinux.org/}{Archlinux} distribution.}

		\ressubitem{Experience with \texttt{rpm}, \texttt{dpkg}, \texttt{tar} 
		and other package management systems, as well as frontends to those.}

        \resitem{\textbf{LFS:} built a GNU/linux software distribution from 
		``scratch'' under the instruction of the 
		\href{http://www.linuxfromscratch.org/lfs}{\underline{Linux From 
		Scratch}} Project. This invloves partitioning, setting up file systems,
		retrieving sources for all system packages, building a temporary and 
		then permanent C/C++ toolchain, building/configuring packages, setting 
		up virtual nodes for initial devices and finally setting up the user and 
		boot sequences for that system.}

		\ressubitem{In short, Linux is \textbf{fun} to learn and work with.}
        %    \resitem{\textbf{Previous interactions:} I've had limited interaction with Fedora, Debian, Gentoo, and FreeBSD--in 
        %    installing, package management and some general use.}
        %    \resitem{\textbf{Other OS's:} Lastly, I've used Windows XP for 6 years (and on and off since), and Mac OS X for 3 years.}
    \end{reslist}
    \begin{reslist}{\textbf{Computer Systems---Tools:}}
		\ressubitem{\textbf{Web Design:} Experience with jQuery, Ruby On Rails,
		Twitter Bootstrap, Angular, some \href{http://documentcloud.github.com/
		backbone/}{Backbone.js}.}
%        \ressubitem{\textbf{Programming:} I have sampled and used a few different programming languages, mostly for scripting. This includes:}
%            \begin{itemize}
%                \item{Bash scripts}
%                \item{Ruby}
%                \item{C++}
%            \end{itemize}
        \ressubitem{\textbf{\LaTeX{}:} Experience with \LaTeX{}, used for professional documentation.}
    \end{reslist}
    \resitem{\textbf{Music:} I've played trumpet for the last 10 years, which has not only been fun but has had me 
        working with people of all different kinds.}


%	\begin{reslist}{Computer Languages:}
%
%		\ressubitem{Proficient in C, C++, HTML, Java, \LaTeX, PHP, UNIX Shells}
%
%		\ressubitem{Familiar with Perl, SQL}
%
%	\end{reslist}
%
%	\begin{reslist}{Tools and Systems:}
%
%		\ressubitem{Proficient in Apache, BIND, CVS/RCS, Make, GnuPG, SSHD, VI}
%
%		\ressubitem{Familiar with Kerberos, MySQL, NFS, OpenLDAP, OpenSSL, Postfix, Samba}
%
%	\end{reslist}


\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

    \begin{ressubsec}{Los Medanos Community College}{Pittsburg, CA}{Computer 
			Science, 2008--present}
		\ressubitem{Completion of classes pertaining to basic programming and 
		Object-oriented programming in C++, programming logic and design, 
		Network Operating Systems, and Web design in html, css, the Dreamweaver
		IDE, and basic Flash programming.}

        \ressubitem{Eligible for the Web Design certificate.}

        %\ressubitem{Participated in the Los Medanos College Jazz and Concert Bands, 2008-2010.}

    \end{ressubsec}

	\begin{ressubsec}{Antioch High School}{Antioch, CA}{Started 2004, Graduated 2008}
%        \begin{reslist}{Participated in:}
%            \resitem{Marching Band 2004-2008, trumpet section leader 2007--2008}
%            \resitem{Concert Band 2004-2008}
%            \resitem{Jazz Band 2006-2008}
%            \resitem{East County Honor Band twice, approx. 2005, 2007}
%        \end{reslist}
        \ressubitem{Participated in: Marching Band/Concert Band 2004--2008, Jazz Band 2006--2008, East County Honor Band approx. 2005, 2007, brass section leader 2007--2008}
        \ressubitem{John Philip Sousa Band Award, 2008}
		\ressubitem{Golden State Merit Diploma}
	\end{ressubsec}

\end{ressection}



\begin{ressection}{Volunteer Experience}

    \resitem{\textbf{Thanksgivings Day:} I've voluntered time over many thanksgivings at the American Legion Hall in Antioch, preparing and serving food. 2001-present.}	
    \begin{ressubsec}{Computer Technitian}{(Self-Employed)}{Computer Services: 2009--present}
		\ressubitem{I've troubleshooted problems for home users, from desktop software tweaks and network to hardware upgrades.}
        %\ressubitem{While people pay if they can, I'm willing to volunteer my time in some cases and trade services in others.}
	\end{ressubsec}

    \resitem{\textbf{Marching Band:} After graduating, I continued to help the band with organizing events, serving food and many other tasks. 2008-2011.}
    \resitem{\textbf{Youth Group:} I participated in and led a youth group at Golden Hills Community Church, approx. 2003-2007}


\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Achievements and Activities}

%	\resitem{Served a voluntary two-year mission in Serbia and Bulgaria (2001--2003).  Speak fluent Serbian and basic Bulgarian.}
%
%	\resitem{As a member and president of the BYU Unix Users Group, assist new Linux users and participate in presentations and discussions on advanced topics (2003--present).}
%
%	\resitem{Manage a heterogeneous home network and family server (1996--present).}
%
%	\resitem{Received a National Merit Scholarship.}
%
%	\resitem{Co-authored ``Interacting Quantitative Trait Loci Control Phenotypic Variation in Murine Estradiol-Regulated Responses,'' \textit{Endocrinology} 140 no. 2 (1999).}
%
%	\resitem{Awarded Eagle Scout Rank, Boy Scouts of America (1996).}


%\end{ressection}


\end{document}
